\documentclass[12pt,twoside,openany]{book}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{color}
\usepackage{amsmath,amssymb}
\usepackage{float}
\usepackage[hyphens]{url}
%\usepackage{bigints,relsize}
\usepackage{mathrsfs,mathtools,xfrac}
%\usepackage{mathtools,xfrac}
%\usepackage{subfig} % needed for proper size caption in Table A.1
\usepackage[T1]{fontenc}
\usepackage{mathptmx} % needed to make text and equations in Times New Roman 
%\usepackage{times}
\usepackage{aastex_hack,natbib}
\usepackage{deluxetable}
%\usepackage{tabularx}
\usepackage{rotating,rotate}
\usepackage{pdflscape,longtable}
\usepackage[toc,page]{appendix}
%\usepackage{fixmainmatter} % I created this pkg to fix the blank page issue in \mainmatter
\usepackage{rotating} % Provides {sideways}{sidewaysfigure}{sidewaystable} environments
%\documentclass{aastex}
\usepackage{grffile}
%\usepackage{epstopdf}
\usepackage{lscape}
\usepackage{natbib}
\usepackage{xr}
\usepackage{url}
%\usepackage{hyperref}
\usepackage{caption}
\usepackage[caption=false]{subfig}
%\usepackage{float,lscape}
%\usepackage{pdflscape}
%\usepackage{equation}
%\usepackage{fancyhdr}
%\captionsetup[deluxetable]{labelformat=empty}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{bm}
\usepackage{cancel}
\usepackage{epstopdf}
\usepackage{accents}
\usepackage{multicol}
%\usepackage{listing}
% XXX CHECK THIS IS OK!
\bibstyle{apj_w_etal}

\DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}
%\setlength{\topmargin}{0.9in}
\setlength{\hoffset}{0.05in}
\setlength{\textheight}{8.5in}
\setlength{\headheight}{0in}
\setlength{\headsep}{-.22in}
\setlength{\oddsidemargin}{0.55in}
\setlength{\evensidemargin}{0.55in}
\setlength{\textwidth}{5.9in}
\newcommand{\doublespaced}{\renewcommand{\baselinestretch}{2}\normalfont}
\newcommand{\singlespaced}{\renewcommand{\baselinestretch}{1}\normalfont}
\newcommand{\halfspaced}{\renewcommand{\baselinestretch}{1.5}\normalfont}
\renewcommand{\arraystretch}{0.7}
\newcommand*\rfrac[2]{{}^{#1}\!/_{#2}}
\newcommand{\avg}[1]{\ensuremath{\langle #1 \rangle}}
\newcommand{\Ang}{\; \mathring{\text{A}}}
\newcommand{\Lya}{Ly$\alpha$ }
%\newcommand{\Ang}{\mbox{ \AA}} 
\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}
\makeatletter
\newcommand{\unchapter}[1]{%
  \begingroup
  \let\@makechapterhead\@gobble % make \@makechapterhead do nothing
  \chapter{#1}
  \endgroup
}
\makeatother

%force sub subsections to be numbered and show show up in the table of contents

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
% define some shortcuts
\newcommand{\Fig}[1]{Fig.~\ref{#1}}
\newcommand{\Sec}[1]{Section~\ref{#1}}
\newcommand{\Eqn}[1]{Eq.~\ref{#1}} \newcommand{\lya}{Ly$\,\alpha$ }
\newcommand{\trec}{\ensuremath{t_{\rm rec}}}
\newcommand{\tq}{\ensuremath{t_{\rm q}}}
\newcommand{\nbar}[1]{\ensuremath{\bar{n}_{\rm #1}}}
\newcommand{\pow}[2]{\ensuremath{#1 \times 10^{#2}}}
\newcommand{\hmpc}{\ensuremath{\,h^{-1}\,{\rm Mpc}\,}}
\newcommand{\ihmpc}{\ensuremath{\,h\,{\rm Mpc^{-1}}}}
\newcommand{\K}{\mbox{ K}}
\newcommand{\bma}{\begin{math}}
\newcommand{\ema}{\end{math}}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\beqa}{\begin{eqnarray}}
\newcommand{\eeqa}{\end{eqnarray}}
\newcommand{\bc}{\begin{center}}
\newcommand{\ec}{\end{center}} 
\newcommand{\bit}{\begin{itemize}}
\newcommand{\eit}{\end{itemize}}
\font\BFd=cmmib10
\font\BFt=cmmib10
\font\BFs=cmmib10 scaled 700
\font\BFss=cmmib10 scaled 500
\def\bbox#1{%
\relax\ifmmode
\mathchoice
{{\hbox{\BFd #1}}}
{{\hbox{\BFt #1}}}
{{\hbox{\BFs #1}}}
{{\hbox{\BFss #1}}}
\else \mbox{#1} \fi }
\def\k{{\bbox{k}}}
\def\q{{\bbox{q}}}
\def\r{{\bbox{r}}}
\def\x{{\bbox{x}}}
\def\thetab{\pmb{\theta}}
\def\dk{\frac{d^3k}{2 \pi^3}}
\def\dq{\frac{d^3q}{2 \pi^3}}
\def\dkc{\frac{d^3k_3}{(2 \pi)^3}}
\newcommand{\MHz}{\mbox{MHz}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\tita}{{\bf OUTER SPACE AND FOURIER SPACE}:\\UNDERSTANDING FOREGROUNDS FOR NEUTRAL HYDROGEN\\EPOCH OF REIONIZATION MEASUREMENTS}
\newcommand{\titlow}{Outer space and Fourier space:\\ understanding foregrounds for neutral hydrogen Epoch of Reionization measurements}

\begin{document}
\addcontentsline{toc}{chapter}{Title}
\frontmatter
\doublespaced
\thispagestyle{empty}
\parskip=0.3in
\begin{center}
{\tita }\\

Saul Aryeh Kohn\\

A DISSERTATION\\

in\\ 

Physics and Astronomy\\

Presented to the Faculties of the University of Pennsylvania \\
in Partial Fulfillment of the Requirements for the Degree of Doctor of Philosophy\\

2018
\end{center}
\parskip=0in

\begin{multicols}{2}
\noindent Supervisor of Dissertation \\

\begin{flushright}
\noindent Graduate Group Chairperson\\
\end{flushright}

\end{multicols}

\noindent\makebox[0in][l]{\rule[2ex]{2.8in}{.3mm}} \hspace{3.05in} \makebox[0in][l]{\rule[2ex]{2.8in}{.3mm}} 
\vspace{-.5in}
\begin{multicols}{2}
\singlespaced
\noindent James E. Aguirre\\ \small Associate Professor of Physics and Astronomy\\

\normalsize

%this is the grad chair, not the chair of the committee, right?
\begin{flushright}
Joshua Klein\\ \small Professor of Physics and Astronomy
\end{flushright}
\end{multicols}

\halfspaced
\noindent Dissertation Committee:

\noindent Cullen Blake, Assistant Professor of Physics and Astronomy

\noindent Adam Lidz, Associate Professor of Physics and Astronomy

\noindent Elliot Lipeles, Associate Professor of Physics and Astronomy

\noindent Masao Sako, Associate Professor of Physics and Astronomy

\newpage

\pagestyle{plain}
\unchapter{Dedication}
\doublespaced
\vspace*{2in}
\begin{center}
{\large\emph{to my grandparents}}
\end{center}

\newpage

%\doublespacing

\thispagestyle{empty} % No page number as per Manual, p. 11

\vspace*{\fill}

\begin{flushleft}
{\tita }

\copyright \space COPYRIGHT
 
2018

Saul Aryeh Kohn\\[24 pt] % If traditional copyright then delete everything below here, but keep \end{flushleft}

This work is licensed under the \\
Creative Commons Attribution \\
NonCommercial-ShareAlike 3.0 \\
License

To view a copy of this license, visit

\url{http://creativecommons.org/licenses/by-nc-sa/3.0/}
\end{flushleft}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Acknowledgments}
\halfspaced

% intro...
While I am the one to have performed the research and compiled it, this thesis is the product of many, of which I must thank a specific few. 

% PAPER & HERA teams
It has been a privilege to work alongside the talented and passionate individuals that comprise the PAPER and HERA teams. My co-conspirators of PAPER analysis -- Danny Jacobs, Carina Cheng, Matt Kolopanis and Josh Kerrigan -- it has been a struggle and a pleasure, and I will sorely miss working with you.

The Department of Physics \& Astronomy of the University of Pennsylvania is a fantastic place to work. The cohorts of graduate students it brings together are consistently awesome, innovative and friendly. I have made my best friends here, including (but not limited to) Ashley Baker, Christian Herwig, Elodie Resseguie, Christina Krawiec, Rachel Wolf and Alyssa Barlis. Outside of Physics \& Astronomy, but within the Penn umbrella, I must thank my dear friends Julie Westover, Irteza Binte-Farid and Steve Kocher for their sturdy support.

James, you are \textit{the best} supervisor. I have learned so much from you, and treasure the opportunities you have given me to grow and become the scientist that I am. I know how rare it is to be able to call a PhD supervisor a friend, and I count my luck there daily.

I have an awesome family, which is about to double in size! Matt and Debbie, thank you for great conversations, encouraging words and hospitality. I can't want to be your son-in-law.

Hannah, Yosef and Ezra, you are are always full of loving support and cutting sarcasm, neither of which I ever want to be without.

Mom and Dad, this thesis belongs to you as much as it does me. Your hard work, encouragement and love made me who I am. Thank you.

Gabby -- you're the best, and I love you. What more can I say? I'll save the good stuff for the wedding.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\newpage
%\vspace*{.75 in}
\vspace*{.15 in}
\begin{center}
\addcontentsline{toc}{chapter}{Abstract}
{\bf ABSTRACT}\\
\tita \\
\parskip=0.2in


Saul A. Kohn\\
James E. Aguirre
\end{center}
\noindent
%350 Word Limit
%Write One
Abstracts are written last.

\vspace*{\fill}

\newpage

\singlespaced
\tableofcontents

%% WARNING - TABLES ARE BEING NUMBERED WEIRDLY!!!
%% LISTED NUMBER DOES NOT MATCH THE \ref NUMBER GIVEN
%% BY BIBTEX OR WHATEVER!!!

\newpage
\phantomsection
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables

\newpage
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures


\halfspaced
\setlength{\parindent}{0.25in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\mainmatter
\part{Radiation, Interferometry \& Polarimetry}

\vspace*{\fill} 
\begin{quote} 
\centering 
... His light is like a niche, within which is a lamp, the lamp within glass, the glass as if it were a white star... Light upon light.\\
\textit{Al Quran, Surah An Nur (24:35)}
\end{quote}
\vspace*{\fill}

\include{chapters/eor_intro/eor_intro} % The Epoch of Reionization
%
% what is the EoR
% why is it interesting (near term) - Liu Tau constraints, Kittiswitt maps, Kern emulators
% current (CMB, high-z galaxies, HI limits, AHEM AHEM KSZ) and future (HI, CO, C+ intensity mapping, extreme deep fields from JWST) probes
% why are we still looking => foregrounds
% in the following chapters I will speak about...
%
\include{chapters/astropol/astropol} % Astrophysical Radiation
%
% synchtrotron & bremstrahlung
% GSM 2008, 2017
% what is polarization (emag) -- STOKES PARAMETER DEFINITIONS
% sources of astrophysical polarization
% magnetic fields and rotation measures
% oppermann map -- high RM point sources
% Lenc, Jelic, etc. diffuse low RM stuff
%
\include{chapters/interferometry/interferometry} % Interferometry
%
% building the [classical] visibility equation in the unpolarized case
% pointing vs drift-scanning
% wide field effects
% rebuilding the visibility equation for widefield, polarized instruments
% imaging example?
%%% basics of calibration for drift-scanning interferometers
% redundant calibration theory; firstcal
% redundant vs imaging configurations
% CLEAN

%%% Instrumental polarization:
% explore the matrix-formalized visibility equation
% DI leakage
% DD leakage
%
\include{chapters/instruments/instruments}
%
% change rcvr -> hut to 50 Ohm
%
\part{Structure in Fourier space}

\vspace*{\fill} 
\begin{quote} 
\centering 
The Gemara asks: Do we not see that comets pass Orion? The Gemara rejects this: The aura of the comet passes Orion and it appears as though the comet itself passes. Rav Huna, son of Rav Yehoshua, said a different answer: It is merely that veil, one of the firmaments, rips and furls and the light of the next firmament is seen, and this appears like a comet. Rav Ashi said another explanation: It is not a comet that passes Orion, but a star that is uprooted from one side of Orion, and another star, from the other side of Orion, sees it and gets startled and shudders, and appears as if it is passing.\\

\textit{Talmud Berakhot (58b:11)}
\end{quote}
\vspace*{\fill}

\include{chapters/eor_window_theory/eor_window_theory}
%
% -- sort of a lit review chapter --
% The issue of low frequency foregrounds for EoR measurements
% Define power spectra...
% foreground wedge and EoR window -- Nithya predictions
% Foreground avoidence: delay spectrum
% Foreground subtraction: theory and LOFAR results
% Hybrid approach: MWA
% polarization in wedge space -- my nice freq vs fourier space diagram? -- basically everything from Moore 2013
%
% in the following chapters I will speak about... ALL MY WORK
%
\include{chapters/data_processing/data_processing}
%
%
%
\include{chapters/polcal/polcal}
%
% more discussion of what degeneracies are and how they get fixed
% only use the high band in power spectra
%  --> all done except for the two above points
%
\include{chapters/ionosphere/ionosphere}
% 
% bridge to EoR window studies?
%
\include{chapters/eor_window_PAPER/eor_window_PAPER}
%
%
%
\include{chapters/eor_window_HERA/eor_window_HERA}
%
% - figure out where DI/DD leakage is reviewed vs pushed to previous chapters
% - describe simulations accordingly
%
\include{chapters/psa128_pol/psa128_pol} % move above HERA?
%
%
%
\part{Expanding the potential of EoR measurements}


\vspace*{\fill} 
\begin{quote} 
\centering 
There is one glory of the sun, and another glory of the moon, and another glory of the stars; for star differs from star in glory. \\
\textit{1 Corinthians (15:41)}
\end{quote}
\vspace*{\fill}


% other stuff -- needs a brief non-chapter introduction
\include{chapters/global_signal/global_signal}
%
% be upfront about Question in the field about whether this IS possible
% our argument -> Cls
% others: mutual coupling
% future work: how to tell the difference? are they actually the same thing (you need a PB w/ directivity along baseline direction =?= mutual coupling
%
% divide data by Rogers & Bowman i.e. normalize to flat sky spectrum, then divide by PLP sim
% look at TAV of Zac PAPER sim (from omnipolcal)
%
% HERA TAV?
%
% theory and observation of PAPER and HERA time-averaged visibilities
% crosstalk memo goes here better than in QA?
%
\include{chapters/ksz_21cm/ksz_21cm}
%
% kSZ theory, link to EoR
% bispectrum & trispectrum squeezed formalisms & limitations
% 21cm fg noise in image space (paul memo)
%
% Bispectrum:
% JEA - wants quantitative check (somehow) of semi-analytic method
% - S/N naive estimate
% compare semi-analytic method to Ma, Komatsu et al.?
%
% Trispectrum:
% - filtering stages images
% 
%
\include{chapters/hera_ml/hera_ml}
%
% CNNs on 21cmFAST - regression
% CNNs on 21cmFAST - Sultan's classification
%
\include{chapters/conclusion/conclusion}
%
% where to go next
%


%\appendix
\begin{appendices}
%\addcontentsline{toc}{chapter}{Appendices}
\include{appendices/software}

\end{appendices}

\newpage
%\include{bibliography}
%\chapter{Bibliography}
%!!!!! XXX
\bibliographystyle{apj_w_etal}
\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{thesisbib}

\end{document}
